---
title: "Introduction to My R Package MATH4753Lacsamana2024"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753Lacsamana2025)


```

# Description

This R package contains various statistical functions used throughout the mini labs done over the course of the semester. I have provided examples of some of these functions and their outputs below. Additionally, the package includes documented data, specifically a fire data file.

# R Data

## Fire Data

Check fire.R for description and notations.
```{r}
head(fire)
```

# R Functinos

## mybinomial.R

Returns a table of the number of success and a barplot of the number of successes. Check mybinomial.R for description
```{r}
mybin(iter=1000,n=18, p=0.3)
```

## myboo2.R

Returns a list containing pertinent info the bootstrap function has measured


```{r}
set.seed(39)
sam=rnorm(25,mean=25,sd=10)
myboot2(iter=1000,x=sam,fun="mean",alpha=0.05)
```

## mycltu.R

Returns a histogram displaying the runif sample made with the given params. Check mycltu.R for further documentation
```{r}
mycltu(30, 10000, 0, 10)
```

## mycurve.R

Returns graphs the curve givem the params. Check mycurve.R for futher documentation.
```{r}
mycurve(5, 2, 7)
```







